\documentclass[8pt]{res}
\usepackage{ulem}
\usepackage[T1]{fontenc}
\usepackage[none]{hyphenat}
\usepackage[default]{lato}

\setlength{\parskip}{1pt}
\setlength{\parsep}{0pt}
\setlength{\headsep}{0pt}
\setlength{\topskip}{0pt}
\setlength{\topmargin}{0pt}
\setlength{\topsep}{0pt}
\setlength{\partopsep}{0pt}
%\renewcommand*\familydefault{\sfdefault}
%\setlength{\textwidth}{5.1in}

\name{\centerline{\large\bf\Huge Angel G. Alvarez}}
\address{500 Memorial Drive Room \small{\#}205, Cambridge, MA 02139 \\ (916) 756 - 7134}
\address{ \hfill alvareza\small{@}mit.edu \\ \hfill \uline{web.mit.edu/alvareza/www}}
\begin{document}

\opening

\vspace{-1em}

\section{EDUCATION} 
  {\sl Massachussetts Institute of Technology}               \hfill Cambridge, MA\\
    B.S. Candidate, Computer Science and Engineering         \hfill June 2020\\
    GPA 4.8/5.0 \\

  {\sl Natomas Pacific Pathways Prep Charter High School}    \hfill Sacramento, CA \\
    GPA 4.12/4.0                                             \hfill September 2012 - June 2016

\vspace{-1em}

\section{EXPERIENCE}
  {\sl MIT TechX Developer Operations}                       \hfill  Cambridge, MA\\
  Lead Developer                                             \hfill  September 2016 - Present 
    \begin{itemize}  %\itemsep -2pt %reduce space between items
      \item Developed gallery web application for the TechX organization to showcase projects made by the MIT community. 
      \item Utilized Node.js for building a backend, MongoDB for database, and Semantic UI for frontend framework.
      \item Sparked interest in web application from internal dev ops, modified application to accomodate needs of all of TechX.
    \end{itemize} 
  {\sl MIT TechX ProjX}                                      \hfill  Cambridge, MA\\
  Internal Committee Lead                                    \hfill  September 2016 - Present 
    \begin{itemize}  %\itemsep -2pt
      \item Coordinated with a team to review approximately 100 project applications per term. Organized events to connect makers with the MIT community.
      \item Created website for events using Node.js and Express backend.
      \item Orchestrated audio/visual technical services for ProjX events.
      \item Organized first ProjX Expo event, with an attendance in excess of over 200 students.
    \end{itemize}
  {\sl 6.148 Web Programming Competition}                    \hfill  Cambridge, MA\\
  Participant                                                \hfill  January 2017 
    \begin{itemize}
      \item Built full stack web application in competition against hundreds of MIT students.
      \item Explored unorthodoxed methods of connecting ideas through structured graphs.
      \item Finished competition as a semifinalist.
    \end{itemize}

\vspace{-1em}

\section{LEADERSHIP AND ACTIVITIES}
  {\sl Student Information Processing Board}                 \hfill  Cambridge, MA\\
  Executive Committee Member                                 \hfill  August 2016 - Present
    \begin{itemize}  %\itemsep -2pt %reduce space between items
      \item Served as publicity director to develop club relationship with the MIT community.
      \item Fostered campus awareness for club goals through event organization and publicity campaigns.
      \item Increased public awareness to changes in MIT's computing infrastructure. Gained over 500 signatories for petition to administration.
    \end{itemize}
  {\sl Next House Judicial Committee}                        \hfill  Cambridge, MA\\
  Wing Representative                                        \hfill  September 2016 - September 2017
    \begin{itemize} %\itemsep -2pt
      \item Managed budget for dorm wing to organize community building wing events.
      \item Served as liaison between the dorm's residents and government.
    \end{itemize}
    
\vspace{-1em}

\section{SKILLS}
  Java, Python, JavaScript, Haskell, Git, Bash, \LaTeX{}, HTML, CSS, MongoDB, Vim.
\vspace{-1em}

\section{ACADEMIC HONORS} 
  AP Scholar with Distinction, National Honor Society, National Hispanic Recognition Program.

\end{document}
